# Overview {.unnumbered}

This is an R Manual for Adam Loy's section of Applied Regression Analysis (Stat 230) taught in Fall 2025.

This document is intended to help describe how to undertake analyses introduced as examples in the Third Edition of the *Statistical Sleuth* (2013) by Fred Ramsey and Dan Schafer. More information about the book can be found at http://www.proaxis.com/~panorama/home.htm.  

This work adapts work done by Linda Loi, Ruobing Zhang, Kate Aloisio, and Nicholas J. Horton. Their work leveraged initiatives undertaken by Project MOSAIC (http://www.mosaic-web.org), an NSF-funded effort to improve the teaching of statistics, calculus, science and computing in the undergraduate curriculum. 


## Textbook

*The Statistical Sleuth*, third edition by Ramsey and Schaffer


## Data sets

The data sets provided by the textbook authors an be accessed through the {Sleuth3} R package. Once you have installed the package (which is already on our server), you can access the data sets using the `data()` command:

```{r}
# Example loading the data set for Case study 1 in Chapter 1
data("case0101", package = "Sleuth3")
```



## R packages

My goal is to teach you a realistic set of R packages for statistical modeling that are powerful, yet have low overhead. To this end, we will use numerous add-on packages throughout the term. 

:::callout-warning
The list below will be updated throughout the term.
:::

```{r message=FALSE, warning=FALSE}
# Runnning list of R packages
library(ggformula) # data viz
library(mosaic)    # summary stats, etc.
library(dplyr)     # data wrangling
library(car)       # convenient functions for regression modeling
library(broom)     # formatting/extracting regression output
```



All of these pacakges have already been installed on maize.
